Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-12 main_paper.tex
Make small changes to wording in introduction

Just as in CCT, our bias correction step introduces additional
variability. However, the second order polynomial again adequately estimates the
features of the true DGP that are necessary for estimating and accommodating that
additional variability. So we propose
an iterated bootstrap procedure \citep{hall1988}: use the second order
polynomial bootstrap to produce many bootstrap replications of the bias
corrected estimator, and then use the resulting bootstrap distribution to
produce confidence intervals. This procedure, which requires bootstrapping the
datasets produced by an initial bootstrap, is described in Algorithm~\ref{Alg2}
and the resulting confidence intervals are shown to be asymptotically valid in
Theorem~\ref{T2}.

The methods presented in this paper are intended as a ``proof of concept'' that
demonstrates that the analytical correction proposed by CCT can also be
implemented through a new bootstrap procedure. We believe that this procedure is
promising because it can allow applied researchers to construct
accurate confidence intervals in settings where unusual forms of dependence
would make it difficult to derive CCT's analytical correction---the dependence
can be accommodated in principle by modifying the resampling algorithm to one
that matches the dependence in the dataset. The specific version of the bootstrap
presented in this paper, however, does not achieve that level of generality yet,
and one limitation should be noted in particular. The confidence
intervals produced by this bootstrap depend on two separate bandwidth parameters
that must be generated elsewhere. Since these bandwidths are generated using
analytical methods, the confidence intervals could easily be produced using the
same methods. Moreover, in this paper we focus on the baseline case of
sharp RD with a local linear model, however, the results and procedures can be
easily extended to the general local polynomial and higher order derivatives
cases (e.g., Regression Kink Designs, see \citealp{card2009b}, and
\citealp{CardEtAl1,CardEtAl2}).

>>>>

Just as in CCT, our bias correction step introduces additional
variability. However, the second order polynomial again adequately estimates the
features of the true DGP that are necessary for estimating and accommodating that
additional variability. So we propose
an iterated bootstrap procedure \citep{hall1988}: use the second order
polynomial bootstrap to produce many bootstrap replications of the bias
corrected estimator, and then use the resulting bootstrap distribution to
produce confidence intervals. This procedure, which requires bootstrapping the
datasets produced by an initial bootstrap, is described in Algorithm~\ref{Alg2}
and the resulting confidence intervals are shown to be asymptotically valid in
Theorem~\ref{T2}.\footnote{%
  Since our bootstrap resamples the residuals but not the running variable, many
  of the quantities used to prodcue the estimates do not change under the
  bootstrap distribution and can be reused from the original
  estimate. Exploiting this feature makes the iterated bootstrap much less
  computationally burdensome; see the discussion following
  Algoritnm~\ref{Alg2}.} %

The methods presented in this paper are intended as a ``proof of concept'' that
demonstrates that the analytical correction proposed by CCT can also be
implemented through a new bootstrap procedure.  This procedure is promising
because it, like other bootstrap methods, can allow applied researchers to
construct accurate confidence intervals in settings where correct formulas for
the asymptotic variance have not yet been derived, as can be the case when there
is an unusual form of dependence---the dependence
can be accommodated in principle by modifying the resampling algorithm to one
that matches the dependence in the dataset. The specific version of the bootstrap
presented in this paper, however, does not achieve that level of generality,
and one limitation should be noted in particular. The confidence
intervals produced by this bootstrap depend on two separate bandwidth parameters
that must be generated elsewhere. Since these bandwidths are generated using
analytical methods, the confidence intervals could easily be produced using the
same methods. Moreover, in this paper we focus on the baseline case of
sharp RD with a local linear model, however, the results and procedures can be
easily extended to the general local polynomial and higher order derivatives
cases (e.g., Regression Kink Designs, see \citealp{card2009b}, and
\citealp{CardEtAl1,CardEtAl2}).
